Multi-modality Imagery Database for Plant Phenotyping

### 2015-04-29 datapapr_labeling.tex
xm's first edits

As shown in Tab.~\ref{tab:database}, MSU-PID can be used for leaf segmentation, leaf alignment, leaf tracking, and leaf counting.
To facilitate future research, we separate the database into training set and testing set.
$40\%$ of the data is used for training and $60\%$ for testing.
Specifically, $6$ plants of Arabidopisis and $2$ plants of bean are selected for training.
We will provide training and testing data in different folders.
For fair comparison, both supervised learning and unsupervised learning methods should evaluate the performance on the training and testing sets separately.
The evaluation metrics will be discussed in Sec.~\ref{sec:baseline}.

@@

\paragraph{Performance metric}
To evaluate the performance of leaf segmentation, alignment, and tracking, we use four criteria and provide the Matlab implementations.
Three of them are based on tip-based error, which is defined as average distance of a pair of estimated leaf tips $\hat{\bm{t}}_{1,2}$ with a pair of labeled leaf tips $ \bm{t}_{1,2}$ normalized by the labeled leaf length:

\begin {equation}
e_{la}(\hat{\bm{t}}_{1,2}, \bm{t}_{1,2}) = \frac{||\hat{\bm{t}}_1-{\bm{t}}_1||_2 + ||\hat{\bm{t}}_2-{\bm{t}}_2||_2}{2 ||\bm{t}_1-\bm{t}_2||_2}.
\label{eqn:tipError}
\end{equation}

We build the frame-to-frame and video-to-video correspondence respectively and generate two sets of tip-based errors.
More details can be find in~\cite{};
We define a threshold $\tau$ to operate on the corresponding tip-based errors.
By varying $\tau$, we compute the first three criteria as:
\begin{itemize}
  \item {\it{Unmatched Leaf Rate(ULR)}}, the percentage of unmatched leaves w.r.t. the total number of labeled leaves. This can attribute to two sources. First, miss detections and false alarms. Second, matched leaves with tip-based errors larger than $\tau$.
  \item {\it{Landmark Error(LE)}}, the average tip-based errors smaller than $\tau$ of all frame-to-frame correspondent leaves.
  \item {\it{Tracking Consistency(TC)}}, the percentage of video-to-video correspondent leaves whos tip-based errors are smaller than $\tau$.
\end{itemize}

In order to evaluate the leaf segmentation accuracy, we adopt an additional metric~\cite{scharr2014annotated} based on the Dice score of estimated segmentation result and ground truth label:
\begin{itemize}
  \item {\it{Symmetric Best Dice(SBD)}}, the symmetric best Dice among all labeled leaves.
\end{itemize}

The Matlab function for computing {\it{SBD}} is provided by~\cite{scharr2014annotated}.
The instruction on how to use the evaluation functions are included within the functions.

>>>>

As shown in Table~\ref{tab:database}, MSU-PID can be used for applications such as leaf segmentation, leaf alignment, leaf tracking, and leaf counting.
To facilitate future research, we separate the database into the training set and the testing set.
$40\%$ of the data is used for training and $60\%$ for testing.
Specifically, $6$ plants of Arabidopisis and $2$ plants of bean are selected for training.
We will provide training and testing data in different folders.
For fair comparison, both supervised learning and unsupervised learning methods should evaluate their performances on the training and testing sets separately.
The user may decide to utilize one or multiple modalities of the plant imagery for training and testing respectively.
The availability of multiple modalities allows user to design novel experimental setup. 
For example, using RGB and depth modalities for training and RGB for testing can evaluate an algorithm that can handle a missing modality during the testing.
%The evaluation metrics will be discussed in Sec.~\ref{sec:baseline}.

@@

\paragraph{Performance metric}
To evaluate the performance of leaf segmentation, alignment, and tracking, we use four performance metrics, whose Matlab implementations will be provided along with the data.
Three of them are based on the tip-based error, which is defined as the average distance of a pair of estimated leaf tips $\hat{\bm{t}}_{1,2}$ with a pair of labeled leaf tips $ \bm{t}_{1,2}$ normalized by the labeled leaf length:
\begin {equation}
e_{la}(\hat{\bm{t}}_{1,2}, \bm{t}_{1,2}) = \frac{||\hat{\bm{t}}_1-{\bm{t}}_1||_2 + ||\hat{\bm{t}}_2-{\bm{t}}_2||_2}{2 ||\bm{t}_1-\bm{t}_2||_2}.
\label{eqn:tipError}
\end{equation}

We build the frame-to-frame and video-to-video correspondence respectively and generate two sets of tip-based errors.
More details can be find in~\cite{};
We define a threshold $\tau$ to operate on the corresponding tip-based errors.
By varying $\tau$, we compute the first three metrics as follows:
\begin{itemize}
  \item {\it{Unmatched Leaf Rate (ULR)}}, the percentage of unmatched leaves with respect to the total number of labeled leaves. 
This can attribute to two sources. 
The first is miss detections and false alarms. 
The second is matched leaves with tip-based errors larger than $\tau$.
  \item {\it{Landmark Error (LE)}}, the average tip-based errors smaller than $\tau$ of all frame-to-frame correspondent leaves.
  \item {\it{Tracking Consistency (TC)}}, the percentage of video-to-video correspondent leaves whose tip-based errors are smaller than $\tau$.
\end{itemize}

In order to evaluate the leaf segmentation accuracy, we adopt an additional metric~\cite{scharr2014annotated} based on the Dice score of estimated segmentation results and ground truth labels:
\begin{itemize}
  \item {\it{Symmetric Best Dice (SBD)}}, the symmetric best Dice among all labeled leaves.
\end{itemize}
The Matlab function for computing {\it{SBD}} is provided by~\cite{scharr2014annotated}.
The instruction on how to use the evaluation functions are included as comments of the function.
